Manuscript_Github_Pchabaudi_pir

### 2022-08-26 chapter4_results_chabaudi24h/Thesis_Github_Pchabaudi_pirAnalysis.Rmd
Added a TPM filter to the stacked bar chart

```{r all_pir_barchart}
cir_plot <- chab_tpm.df %>% 
  filter(Geneid %in% cir_id) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(time = str_extract(sample, pattern = '[[:digit:]]{2}h|sch.culture'),
         transmission = str_split_fixed(sample, pattern = '_', n = 2)[,1],
         SorL = cir_clade_info$SorL[match(Geneid, cir_clade_info$Geneid)]) %>% 
  group_by(Geneid, time, transmission, SorL) %>% 
  dplyr::summarise(tpm = median(tpm)) %>% 
  arrange(SorL, tpm)

>>>>

```{r all_pir_barchart}
#Filter for pirs above 1 TPM in at least one sample
cir_plot <- chab_tpm.df %>% 
  filter(Geneid %in% cir_id,
         if_any(!matches('Geneid'), ~ . > 1)) %>% 
  melt(id.vars = 'Geneid', variable.name = 'sample', value.name = 'tpm') %>% 
  mutate(time = str_extract(sample, pattern = '[[:digit:]]{2}h|sch.culture'),
         transmission = str_split_fixed(sample, pattern = '_', n = 2)[,1],
         SorL = cir_clade_info$SorL[match(Geneid, cir_clade_info$Geneid)]) %>% 
  group_by(Geneid, time, transmission, SorL) %>% 
  dplyr::summarise(tpm = median(tpm)) %>% 
  arrange(SorL, tpm)
